Technical Report

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
Fix changes I made since Lau pointed out that xreadcond is intended to be used *together* with readcond.

\begin{lemma}
  \label{lem:stareg-ms-subeq-stdreg}
  If
  \begin{itemize}
  \item $R \nequal \stareg[(\ms,\ms)]{\pur}$
  \item $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$
  \item $\dom(\ms) \supseteq [\baddr,\eaddr]$
  \end{itemize}
  Then
  $R \nsubeq \stdreg{\dom(\ms)}{\pur}$
\end{lemma}
\begin{proof}
  \dominique{TODO: define nsubeq and friends first?}
\end{proof}

\begin{lemma}[readXCondition implies readCondition]
  \label{lem:readXCond-readCond}
  If $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, then $\npair{(\baddr,\eaddr)}\in\readCond{\lin,W}$.
\end{lemma}
\begin{proof}
  From $\npair{(\baddr,\eaddr)}\in\xReadCond{\lin,W}$, we get by definition an $r \in \addressable{\lin, \pwheap}$ and an $\ms$ with $\dom(\ms) \supseteq [\baddr,\eaddr]$,  $\npair{(\ms,\ms)} \in H^{\mathrm{std}}_{\dom(\ms)} \; * \; W$ and $\pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}$.

  The result then follows directly using Lemma~\ref{lem:stareg-ms-subeq-stdreg}.
\end{proof}

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$ and $\npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}$.
From Lemmas~\ref{lem:readcond-writecond-work} and~\ref{lem:readXCond-readCond}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

>>>>

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \readCond{\lin,W}
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$, $\npair{(\baddr,\eaddr)}\in \readCond{\lin,W}$ and $\npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}$.
From Lemmas~\ref{lem:readcond-writecond-work}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

### 2018-03-09 fully-abstract-comp/technical-report.tex
Fix readXCond to require that ms is safe.
TODO: xreadCond implies readcond.
Fix changes I made since Lau pointed out that xreadcond is intended to be used *together* with readcond.

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwfree(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad \pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]
\dominique{The above needs to require that $\ms$ contains safe values somehow.}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
% Note: the below FTLR is simpler than the above thanks to the new expression relation relating pairs of caps rather than pairs of pairs of caps. It expresses that any reasonable executable capability is safe to use as the pc capability. 
\dominique{I'm following the example of the previous FTLR by not allowing $\rwx$, but it's not clear to me why that's the right thing to do.}
\begin{theorem}[FTLR]
  \label{thm:ftlr}
  \[
    \begin{array}{l}
      \forall n,W,\lin,\baddr,\eaddr,\aaddr \ldotp \\
      \quad \left(
      \begin{array}{l}
        % \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}
      \end{array}
      \right)\\
      \quad\Rightarrow 
      \npair{\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
                      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray} \in \lre(W)

    \end{array}
  \]
  \dominique{6-3-2018: I removed $\readCond{\lin,W}$ and replaced it with $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
\end{theorem}

>>>>

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists A \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsubeq \stdreg{A}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwfree(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad \pwheap(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]
\dominique{9-3-2018: I changed the above to require that $\ms$ contains safe values by requiring that it is in Hstd. Is this reasonable?}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
% Note: the below FTLR is simpler than the above thanks to the new expression relation relating pairs of caps rather than pairs of pairs of caps. It expresses that any reasonable executable capability is safe to use as the pc capability. 
\dominique{I'm following the example of the previous FTLR by not allowing $\rwx$, but it's not clear to me why that's the right thing to do.}
\begin{theorem}[FTLR]
  \label{thm:ftlr}
  \[
    \begin{array}{l}
      \forall n,W,\lin,\baddr,\eaddr,\aaddr \ldotp \\
      \quad \left(
      \begin{array}{l}
        \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}
      \end{array}
      \right)\\
      \quad\Rightarrow 
      \npair{\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
                      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray} \in \lre(W)

    \end{array}
  \]
  \dominique{6-3-2018: I added $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
\end{theorem}
